\documentclass[12pt]{article}
\oddsidemargin=0truein
\evensidemargin=0truein
\topmargin=0.5truein\headheight=0truein\headsep=0truein
\textheight=9truein\textwidth=6.5truein
\parindent=0cm
\baselineskip=25pt
\renewcommand{\baselinestretch}{1.24}
\parskip=3mm
\renewcommand{\bottomfraction}{0.7}
\usepackage{amsfonts}
\usepackage{verbatim}

\pagestyle{empty}

\begin{document}
{\large
\begin{center}
\it{Curriculum Vitae}\\
\bf{William J. McCausland}\\
\end{center}
}

\subsection*{Contact Information}

\parbox{8cm}{
Mailing Address: \\
\\
D\'epartement de sciences \'economiques \\
C.P. 6128, succursale Centre-ville, \\
Montr\'eal, QC H3C 3J7, Canada \\
}
\parbox{7cm}{
Street Address: \\
\\
Pavillon Lionel Groulx \\
3150 rue Jean-Brillant, C-6046 \\
Montr\'eal, QC H3T 1N8, Canada \\
}

Telephone:  (514) 343-7281 \\
Fax:  (514) 343-7221 \\
E-mail address:  william.j.mccausland@umontreal.ca \\
Website: \verb+https://mccauslw.github.io+

\subsection*{Education}

\begin{tabular}{llll}
1989 & B.A.Sc. & Engineering Science & University of Toronto \\
1992 & M.Eng. & Electrical Engineering & McGill University \\
1996 & M.A. & Economics & University of Toronto \\
2002 & Ph.D. & Economics & University of Minnesota \\
\end{tabular}

\subsection*{Positions}

\begin{tabular}{llll}
2009- & Associate Professor & Universit\'e de Montr\'eal & Montreal, QC\\
2009-2013 & External Affiliate & Centre for the Study of Choice & Sydney, Australia\\
2001- & Researcher & CIREQ & Montreal, QC\\
2001- & Researcher & CIRANO & Montreal, QC\\
2001-2009 & Assistant Professor & Universit\'e de Montr\'eal & Montreal, QC\\
\end{tabular}

\subsection*{Publications}

``Multivariate stochastic volatility using the HESSIAN method,''
{\it Econometrics and Statistics}, 2021,
{\bf 17}, 76-94
(with Shirley Miller and Denis Pelletier)

``Testing the random utility hypothesis directly,''
{\it Economic Journal}, 2020,
{\bf 130}, 183-207
(with Clintin Davis-Stober, A. A. J. Marley, Sanghyuk Park and Nicholas Brown)

``The HESSIAN method for models with leverage-like effects,''
{\it Journal of Financial Econometrics}, 2015,
{\bf 13}, 722-755.
(with Gbowan B. Djegn\'en\'e)

``Bayesian inference and model comparison for random choice structures,''
{\it Journal of Mathematical Psychology}, 2014,
{\bf 62-63}, 33-46.
(with A.A.J. Marley)

``Prior Distributions for Random Choice Structures,''
{\it Journal of Mathematical Psychology}, 2013,
{\bf 57}, 78-93.
(with A.A.J. Marley)

``The HESSIAN Method (Highly Efficient State Smoothing, In A Nutshell),''
{\it Journal of Econometrics}, 2012,
{\bf 168}, 189-206.

``Simulation smoothing for state-space models: A computational efficiency analysis,''
{\it Computational Statistics and Data Analysis}, 2011,
{\bf 55}, 199-212.
(with Shirley Miller and Denis Pelletier)

``Economic Modeling and Inference, by Bent Jesper Christensen and Nicholas M. Kiefer,''
{\it International Review of Economics and Finance}, 2010,
{\bf 19}, 793-794.
(book review)

``Discussion on the Paper by Rue, Martino and Chopin,''
{\it Journal of the Royal Statistical Society: Series B}, April 2009,
{\bf 71}, 375-375.

``Random Consumer Demand,'' {\it Economica}, February 2009,
{\bf 76}, 89-107.
 
``Bayesian Inference on Time-Varying Proportions,'' in S. Chib, W. Griffiths, G. Koop and D. Terrell (eds.),
{\it Advances in Econometrics, Volume 23: Bayesian Econometric Methods}.
Bingley, UK: Emerald Books, 2008, 525-544.
(with Brahim Lgui)

``On Bayesian Analysis and Computation for Functions with Monotonicity and Curvature Restrictions,''  {\it Journal of Econometrics}, 2008,
{\bf 142}, 484-507.

``Time Reversibility of Stationary Regular Finite State Markov Chains,''  {\it Journal of Econometrics},
2007,
{\bf 136}, 303-318.

``Using the BACC Software for Bayesian Inference,'' {\it Computational Economics},
2004,
{\bf 23}, 201-218.

``Using Simulation Methods for Bayesian Econometric Models,''  in  David E. A. Giles (ed.), {\it Computer-Aided Econometrics}.
New York: Marcel Dekker, 2003, 209-261. (with John Geweke and John J. Stevens)

``Bayesian Specification Analysis in Econometrics,''  {\it American Journal of Agricultural Economics},
2001,
{\bf 83}, 1181-1186. (with John Geweke)

``Embedding Bayesian Tools in Mathematical Software,''  {\it Proceedings of the International Society for Bayesian Analysis (ISBA)}, 
2000, 165-173.
 (with John Geweke)

\subsection*{Unpublished Papers}

``A Flexible Stochastic Conditional Duration Model,''
(with Samuel Gingras)

``An Illustrated Guide to Context Effects,''
(with Clintin Davis-Stober, A. A. J. Marley and Brandon Turner)

``Testing Axioms of Stochastic Discrete Choice Using Population Choice Probabilities,'' (with Clintin Davis-Stober and A. A. J. Marley)

``Dynamic factor models with stochastic volatility''

``The Ghost in the Machine: Inferring Machine-Based Strategies from Observed Behavior,'' (with Jim Engle-Warnick and John Miller)

\subsection*{Conference Presentations (since 2007)}
``{\it RanCh: An R Package for Abstract Random Choice Analysis},''
2019 Meeting of the Society for Mathematical Psychology,
Montr\'eal, QC,
July 2019.

``{\it An Illustrated Guide to Context Effects},''
2018 Meeting of the Society for Mathematical Psychology,
Madison, WII,
July 2018.

``{\it Testing the Random Utility Hypothesis Directly},''
European Seminar on Bayesian Econometrics,
New Orleans, LA,
October 2018.

``{\it Testing Axioms of Stochastic Discrete Choice Using Population Choice Probabilities},''
CIREQ Econometrics Conference,
Montr\'eal, QC,
April 2018 (Poster);
NBER-NSF Seminar on Bayesian Inference in Econometrics and Statistics,
Stanford, CA,
May 2018;
2018 Meeting of the Society for Mathematical Psychology,
Madison, WI,
July 2018;
American Statistical Association Joint Statistical Meetings,
Vancouver, BC,
July 2018.

``{\it Joint Sampling of States and Parameters in State Space Models},''
NBER-NSF Seminar on Bayesian Inference in Econometrics and Statistics,
St. Louis, MO,
May 2017.

``{\it Testing Random Utility Using Falmagne's Conditions Directly},''
International Choice Modelling Conference,
Austin, TX,
May 2015;
2015 Meeting of the Society for Mathematical Psychology,
Laguna Beach, CA,
July 2015;
NBER-NSF Seminar on Bayesian Inference in Econometrics and Statistics,
Philadelphia, PA,
May 2016.

``{\it Dynamic Factor Models with Stochastic Volatility},''
European Seminar on Bayesian Econometrics,
Venice, Italy,
October 2016;
8'th International Conference on Computational and Financial Econometrics (CFE 2014),
Pisa, Italy,
December 2014;
NBER-NSF Seminar on Bayesian Inference in Econometrics and Statistics,
St. Louis, MO,
May 2015.

``{\it Bayesian Inference and Model Comparison for Random Choice Structures},''
NBER-NSF Seminar on Bayesian Inference in Econometrics and Statistics,
St. Louis, MO,
April 2013;
47th Annual Meeting of the Canadian Economics Association,
Montreal, QC,
June 2013;
2013 Meeting of the Society for Mathematical Psychology,
Potsdam, Germany,
August 2013;
Conference on Bayesian Methods in Microeconometric Modeling,
Pasadena, CA,
September 2013.

``{\it Multivariate Stochastic Volatility},''
Rimini Conference in Economics and Finance,
Toronto, ON,
August 2012.

``{\it Prior Distributions for Random Choice Structures},''
2012 Meeting of the Society for Mathematical Psychology,
Columbus, OH,
July 2012.

``{\it The HESSIAN Method (Highly Efficient State Smoothing, In A Nutshell)},''
Workshop on Bayesian Inference for Latent Gaussian Models with Applications,
Zurich, Switzerland,
February 2011;
North American Summer Meeting of the Econometrics Society,
Boston, MA,
June 2009;
43rd Annual Meeting of the Canadian Economics Association,
Toronto, ON,
May 2009;
Seminar on Bayesian Inference in Econometrics and Statistics,
Chicago, IL,
May 2008.

``{\it A New Approach to Drawing States in State Space Models},''
13th International Conference on Computing in Economics and Finance,
Montreal, QC,
June 2007.

``{\it Bayesian Analysis and Computation for Functions Subject to Monotonicity and Curvature Restrictions},''
41st Annual Meeting of the Canadian Economics Association,
Halifax, NS,
June 2007;
Seminar on Bayesian Inference in Econometrics and Statistics,
Saint Louis, MO,
May 2007.

%5``{\it Drawing Stochastic Volatility},'' 
%40th Annual Meeting of the Canadian Economics Association,
%Montreal, QC,
%May 2006;
%Financial Econometrics Conference,
%Montreal, QC,
%May 2006;
%Seminar on Bayesian Inference in Econometrics and Statistics,
%Iowa City, IA,
%April 2006.

%``{\it Time Reversibility of Stationary Regular Finite-State Markov Chains},'' 
%American Statistical Association Joint Statistical Meetings,
%Minneapolis, MN,
%August 2005;
%Bayesian Inference and Stochastic Processes 4,
%Varenna, Italy,
%June 2005.

%``{\it The Ghost in the Machine: Inferring Machine-Based Strategies from Observed Behavior},''
%Economic Science Association,
%Montr\'eal, QC,
%June 2005;
%45i\`eme Congr\`es annuel de la Soci\'et\'e canadienne de science \'economique,
%Charlevoix, QC,
%May 2005;
%39th Annual Meeting of the Canadian Economics Association,
%Hamilton, ON,
%May 2005.

%``{\it Time Reversibility or Irreversibility of Asset Return Volatility},''
%North American Summer Meeting of the Econometrics Society,
%Evanston, IL,
%2003;
%37th Annual Meeting of the Canadian Economics Association,
%Ottawa, ON,
%2003;
%43i\`eme Congr\`es annuel de la Soci\'et\'e canadienne de science \'economique,
%Montr\'eal, QC,
%2003;
%CIREQ-CIRANO-MITACS Financial Econometrics Conference,
%Montr\'eal, QC,
%2003.

%``{\it Bayesian Inference for a Theory of Random Consumer Demand},'' 
%Joint Statistical Meetings (JSM) of the American Statistical Association (ASA),
%New York, NY,
%2002;
%Seventh Valencia International Meeting on Bayesian Statistics,
%Tenerife, Spain,
%2002.

%``{\it BACC Software Demonstration},'' 
%Seventh Valencia International Meeting on Bayesian Statistics,
%Tenerife, Spain,
%2002.

%``{\it A Theory of Random Consumer Demand},'' 
%Canadian Economic Theory Conference,
%Toronto, ON,
%2002.

%``{\it Random Consumer Demand: Theory and Inference},'' 
%International Society for Bayesian Analysis Regional Meeting,
%Laguna Beach, CA,
%2001.

\subsection*{Discussions (since 2007)}

``{\it Disccussion of Lee, Liau, Seo and Shin, Factor-Driven Two-Regime Regression},''
Canadian Econometrics Study Group,
Montr\'eal, QC,
2019.

``{\it Discussion of Creel, Gao, Hong and Kristensen, Bayesian Indirect Inference and the ABC of GMM},''
CIREQ Econometrics Conference.
Montr\'eal, QC,
2018.

``{\it Discussion of Jin and Maheu, Bayesian Semiparametric Modeling of Realized Covariance Matrices},''
Canadian Econometrics Study Group,
Guelph, ON,
2015.

``{\it Discussion of Burda and Prokhorov, Copula Based Factorization in Bayesian Multivariate Infinite Mixture Models},''
47th Annual Meeting of the Canadian Economics Association,
Montreal, QC,
2013.

``{\it Discussion of Liu, Markov Switching Quantile Autoregression},''
47th Annual Meeting of the Canadian Economics Association,
Montreal, QC,
2013.

``{\it Discussion of Kiefer, Correlated Defaults, Temporal Correlation, Expert Information and Predictability of Default Rates},''
Third CIREQ Time Series Conference,
Montreal, QC,
2009.
 
``{\it Discussion of Gordon and Amedah, Bayesian Analysis via MCMC Scheme for the Normal Inverse Gaussian},''
41st Annual Meeting of the Canadian Economics Association,
Halifax, NS,
2007.

``{\it Discussion of van Hasselt, Bayesian Inference in the Sample Selection
and Two-Part Models},''
Canadian Econometrics Study Group,
Montreal, QC,
2007.

%``{\it Discussion of Xu, Stochastic Volatility Model under Discrete Mixtures of Normal Specification},''
%Canadian Econometrics Study Group,
%Niagara Fall, ON,
%2006.

%``{\it Discussion of Gayle and Richard: Numerical Analysis of Asymmtric First Price Auctions with Reserve Prices},''
%39th Annual Meeting of the Canadian Economics Association,
%Hamilton, ON,
%2005.

%``{\it Discussion of Imai, Jain and Ching: Bayesian Estimation of Dynamic Discrete Choice Models},''
%37th Annual Meeting of the Canadian Economics Association,
%Ottawa, ON,
%2003.

%``{\it Discussion of Li, Sarkar and Wang: Diversification Benefits of Emerging Markets Subject to Portfolio Constraints},''
%International Society for Bayesian Analysis Regional Meeting,
%Laguna Beach, CA,
%2001.

\subsection*{Seminar Presentations (since 2007)}

``{\it Axioms and inference: a toolbox for abstract stochastic discrete choice},''
University of Missouri (Department of Psychology), February 2019.

``{\it Testing Random Utility Using Falmagne's Conditions Directly},''
North Carolina State University, October 2016.

``{\it Dynamic Factor Models with Stochastic Volatility},''
Rutgers University, December 2014.

``{\it State-space Duration Models},''
University of Melbourne, April 2013.

``{\it Prior Distributions for Random Choice Structures},''
Australian National University, March 2013;
University of Sydney, March 2013;
Universit\'e de Montr\'eal, Brown bag microeconomics seminar, September 2012.

``{\it Filtering without Particles},''
University of Technology, Sydney, April 2011.

``{\it A Simulation Approach to Random Choice Axioms and Models },''
University of Technology, Sydney, April 2011.

``{\it The HESSIAN Method (Highly Efficient State Smoothing, In A Nutshell)},''
Australian National University, April, 2011;
Monash University, April 2010;
University of Technology Sydney (CenSoC), April 2010;
University of Sydney, March 2010;
University of Queensland, March 2010;
Cornell University, April 2008;
University of California, Irvine, April 2008.

``{\it The Ghost in the Machine: Inferring Machine-Based Strategies from Observed Behavior},'' 
Louisiana State University, February 2009.
University of Chicago GSB, February 2008;
University of Nevada, Reno, November 2007.
%Queens University, November 2004;
%North Carolina State University, October 2004.

``{\it Efficient inference for semi-Gaussian state space models},''
Universit\'e de Montr\'eal, November 2007.

%``{\it On Bayesian Analysis and Computation for Functions with Monotonicity and Curvature Restrictions},'' 
%North Carolina State University, October 2006.

%``{\it Bayesian Inference for a Theory of Random Consumer Demand},'' 
%Rutgers University, 2003.

%``{\it Inf\'erence bay\'esienne pour une th\'eorie intrins\`equement stochastique de la demande des consommateurs},'' 
%Universit\'e de Montr\'eal (statistique), 2002.

%``{\it Random Consumer Demand: Theory, Inference and Applications},'' 
%Universit\'e Laval, 2002.

%``{\it D\'emonstration du logiciel BACC},'' 
%Universit\'e Laval, 2002.

%``{\it Using the BACC Software for Bayesian Inference},'' 
%Universit\'e de Montr\'eal, 2001.

\subsection*{Funded Research}

\begin{tabular}{lll}
2013 - 2016
& Australian Research Council (ARC) \\
& Discovery Project (overseas partner investigator) \\
2012 - 2019
& Social Sciences and Humanities Research Council (SSHRC) \\
& Insight Grant (co-applicant)
& \$257,660 \\
2003 - 2006
& Fonds de recherche sur la soci\'et\'e et la culture (FQRSC)
& \$40,500 \\
\end{tabular}

\subsection*{Other Professional Activities}

Referee,
National Science Foundation (USA),
Social Science and Humanities Research Council (Canada),
Deutsche Bundesbank,
Journal of Econometrics,
Journal of Business and Economic Statistics,
Econometric Theory,
Econometric Reviews,
Journal of Applied Econometrics,
Studies in Nonlinear Dynamics and Econometrics,
International Journal of Forecasting,
International Economic Review,
Journal of Economic Theory,
Quantitative Economics,
Economics Letters,
American Journal of Agricultural Economics,
Decisions in Economics and Finance,
Empirical Economics,
Journal of Financial Econometrics,
Canadian Journal of Economics,
Actualit\'e \'Economique,
Computational Statistics and Data Analysis,
Journal of Statistical Computation and Simulation,
Journal of Mathematical Psychology,
Decision,
Psychometrika,
British Journal of Mathematical and Statistical Psychology,
Management Science,
IEEE Signal Processing Letters,
International Journal of Control,
Tourism Management,
International Journal of Mathematical Modelling and Numerical Optimization,
Journal of Statistical Software,
Statistics and Probability Letters

Local organizer, Math Psych 2019, July 19-22, 2019, Montr\'eal.

Co-organizer, with Sean Horan, of 
The CIREQ Montr\'eal workshop on microeconomic theory: foundations of discrete choice models, October 11-12, 2018, Montr\'eal.

Organizer of two sessions at the 43rd annual meeting of the Canadian Economics Assocatiation, 2009.

Program Committee, 24th Canadian Econometrics Study Group Conference, Montreal 2007

External examiner for Fr\'ed\'eric Broussau,
Ph.D. candidate at the Universit\'e du Qu\'ebec \`a Montr\'eal,
defended August 7, 2014.

External examiner for Zhongfang He,
Ph.D. candidate at the University of Toronto,
defended July 22, 2009.

External examiner for Sid Ali Amedah,
Ph.D. candidate at the Universit\'e Laval,
defended June 2, 2008.

\subsection*{Courses Taught}

Mathematical Economics II (ECN 1075), Universit\'e de Montr\'eal

Microeconomic Theory (ECN 2040), Univerit\'e de Montr\'eal

Econometrics I (ECN 2160), Universit\'e de Montr\'eal

Workshop in Applied Econometrics (ECN 3949), Universit\'e de Montr\'eal

Workshop in Applied Economics (ECN 3950), Universit\'e de Montr\'eal

Honours Applied Econometrics (ECN 4160), Universit\'e de Montr\'eal

Elements of Microeconomics (ECN 6013), Universit\'e de Montr\'eal

Microeconomics Workshop (ECN 6053), Universit\'e de Montr\'eal

Numerical Analysis for Economics (ECN 6338), Universit\'e de Montr\'eal

Econometrics of Financial Markets (ECN 6578), Universit\'e de Montr\'eal

Probability for Economists (ECN 6223, ECN 7060), Universit\'e de Montr\'eal

Bayesian Econometrics (ECN 7223B, ECN 7069B), Universit\'e de Montr\'eal

Bayesian Time Series Econometrics (ECN 7069B), Universit\'e de Montr\'eal

Bayesian Econometrics, IMF Institute, Washington, D.C.

\subsection*{Student Supervision}

\subsubsection*{Ph.D.}

Samuel Gingras, ``Essais sur les probl\`emes de d\'ecisions dynamiques et leurs applications,''
May 2021.

Laurent Kemoe, ``Three Essays in Macro-finance, International Economics and Macro-econometrics,''
May 2017, codirected with Hafedh Bouakez (HEC Montr\'eal).

Barnab\'e Djegn\'en\'e,
``Essays on numerically efficient inference in nonlinear and non-Gaussian state space models, and commodity market analysis,''
June 2013, codirected with G\'erard Gaudet (Universit\'e de Montr\'eal).

Shirley Miller Lira,
``Stochastic Volatility: A New Efficient Approach with Applications to Finance and Macroeconomics,''
September 2012, codirected with \'Eric Jaquier (HEC Montr\'eal).

S\'ebastien Blais,
``Analyse bayesienne des mod\`eles de structure \`a terme,''
(Bayesian Analysis of Term Structure Models),
September 2009.

\subsubsection*{M.Sc.}

Guy Arnold Djolaud Kili,
``Model Espace-\'etat: Estimation Bayesienne du NAIRU USA,''
September 2017. (co-supervised with Immo Schott)

Ian Barrett,
``The Responsiveness of Government Revenue to Marginal Tax Rates,''
May 2016.

Abdoul Karim Nchare Fogam,
``Analyse comparative de la pauvret\'e et de la structure de consommation des m\'enages dans la principale agglom\'eration des \'etats membres de l’UEMOA en 2008,''
September 2015. (co-supervised with Marine Carrasco)

D\'esir\'e K\'edagni,
``Identification of inequality measures in selection models,''
August 2015. (co-supervised with Marine Carrasco)

Vladimir Khripunov,
``Estimating preferences with random utility models,''
April 2012.

Mahamadou Morib\'e Sangar\'e,
``La construction des probabilit\'es des \'ev\'enements politiques \`a 
partir des prix dans les march\'es pr\'edictifs,''
(Construction of Probabilities of Political Events from Prices in Predictive Markets)
September 2009.

Fr\'ederic El Cherif,
``A Time Varying Coefficient Model for Changes to an Airline's Stock Price in 
Response to Changes in Prices of Various Futures Contracts for Heating Oil,''
July 2009.

Said Abidoune,
``Volatilit\'e stochastique du taux de change nominal canadien dans une persperctive de long et court terme,''
(Stochastic Volatility of the Nominal Canadian Exchange Rate in a Long- and Short-Term Perspective)
April 2009.

El Housseini Diawlol,
``Une couverture dynamiques sur les futures du carburant : exemple d'Air Canada,''
(Dynamic hedging using fuel futures: the case of Air Canada)
January 2009.

Fran\c{c}ois Rebello,
``L'impact de la responsabilit\'e sociale sur la valeur boursi\`ere des entreprisesÊ: le cas des droits humains,''
(The Impact of Social Responsibility on Firms' Market Capitalization: the Case of Human Rights)
September 2008.

Nguedia Pierre \'Evariste Nguimkeu,
``Bayesian Estimation of Correlation Matrices:
Application to the Multivariate GARCH Model,''
August 2008.

Anderson Walter Nzabandora,
``Estimation bay\'esienne des matrices de corr\'elation : strat\'egies de formulation de lois a priori,''
(Bayesian Estimation of Correlation Matrices: Prior Specification Strategies)
April 2008.

Omar Foutlane,
``Portfolio Risk Analysis and Rebalancing Using a Multifactor Model,''
May 2007.

Oren Tapiero,
``Testing Techniques and Forecasting Ability for FX Options Implied Risk
Neutral Densities'',
May 2007.

Thomas Larouche,
``Comparaison de tests de r\'eversibilit\'e temporelle avec une approche MBBÊ: preuves provenant de s\'eries chronologiques financi\`eres,''
(Comparison of Time Reversibility Tests using a Moving Block Bootstrap Approach: Evidence from Financial Time Series)
June 2006.

Rapha\"el Gendron,
``Analyse bay\'esienne d'un mod\`ele pour les changements de prix de titres \'echanges \`a haute fr\'equence sur les march\'es financiers,''
(Bayesian Analysis of a Price Change Model for High Frequency Stock Exchange
Data)
March 2006.

Constant Aim\'e Lonkeng Ngouana,
``Analyse bay\'esienne des mod\`eles de dur\'ee des transactions financi\`eres de haute fr\'equence,''
(Bayesian Analysis of Duration Models for High Frequency Financial Transactions)
March 2006.

Simon Leblond,
``Comparing Predictive Accuracy of Real Estate Pricing ModelsÊ: An Applied Study for the City of Montr\'eal,''
April 2005.

\end{document}
